The Efficient Handling of Guards in the Design of RPython's Tracing JIT

### 2012-08-15 talk/vmil2012/paper.tex
mention why we expect guards to fail often

%___________________________________________________________________________
\todo{mention somewhere that it is to be expected that most guards do not fail}
\section{Introduction}

@@

\subsection{Overhead of Guards}
\label{sub:guard_overhead}
\begin{figure}
    \include{figures/resume_data_table}
    \caption{Resume data sizes}
    \label{fig:resume_data_sizes}
\end{figure}

@@

\begin{figure}
    \include{figures/backend_table}
    \caption{Total size of generated machine code and resume data}
    \label{fig:backend_data}
\end{figure}

@@

>>>>

%___________________________________________________________________________
\section{Introduction}

@@

\subsection{Space Overhead of Guards}
\label{sub:guard_overhead}
\begin{figure}
    \include{figures/resume_data_table}
    \caption{Resume data sizes}
    \label{fig:resume_data_sizes}
\end{figure}

@@

\begin{figure}
    \include{figures/backend_table}
    \caption{Total size of generated machine code and resume data}
    \label{fig:backend_data}
\end{figure}e.

@@

This low guard failure rate is expected. Most guards do not come from actual
control flow divergences in the user program, but from type checks needed for
type specialization. Various prior work has
shown~\cite{holkner_evaluating_2009, richards_analysis_2010, callau_how_2011}
that most programs in dynamic languages only use a limited amount of runtime
variability. Therefore many guards are needed for making the traces behave
correctly in all cases but fail rarely.
